# Chapter 18 Selected exercises


```{r}
library(rlang)
library(purrr)
```

## 19.3.6 Quoting


1. How is `expr()` implemented ? 

It is simply `\(e) { enexpr(e)}`

2. Compare and contrast two functions below.  Can you predict the output?

(discuss before evaluating)
 
```{r}
f1 <- function(x, y) {
  exprs(x = x, y = y)
}
f2 <- function(x, y) {
  enexprs(x = x, y = y)
}
f1(a + b, c + d)
f2(a + b, c + d)
```

3. Enexpr requires its (immediate) argument to be a symbol not an expression. 

```{r}
(\(x){enexpr(2*x)})(b)
```

If the expression is missing, it returns a 'missing argument' whatever that is. Rlang has a function `is_missing()` to detect that. Copied from the solution:

```{r}
on_missing <- function(x) {enexpr(x)}
on_missing()
is_missing(on_missing())
```

4. Howw are `exprs(a)` and `exprs(a=)` differnet?    
The first one returns a list with a single unnamed elemebt 'a'.  The second returns a list with a single named element $a, with no value. 
 
 
5. `exprs` has more arguments, e.g. `.named` will generate names using for unnamed arguments. 

```{r}
exprs(a, .named = TRUE)
```

6. Skipping


## 19.4.8 Exercises

1. Given the following defintions:

```{r}
xy <- expr(x + y)
xz <- expr(x + z)
yz <- expr(y + z)
abc <- exprs(a, b, c)
```

Use quasiquotation to generate the following calls:

```
(x + y) / (y + z)
-(x + z) ^ (y + z)
(x + y) + (y + z) - (x + y)
atan2(x + y, y + z)
sum(x + y, x + y, y + z)
sum(a, b, c)
mean(c(a, b, c), na.rm = TRUE)
foo(a = x + y, b = y + z)
```

```{r}
expr(!!xy/!!yz)
```

```{r}
expr(-(!!xy)^!!yz)
```

```{r}
expr(((!!xy)) + !!yz - !!xy )
```

Note the double parens. Why?


```{r}
expr(atan2(!!xy,!!yz))
```

```{r}
expr(sum(!!xy,!!xy, !!yz))
```

```{r}
expr(sum(!!!abc))
```

```{r}
expr(mean(c(!!!abc), na.rm = TRUE))
```

```{r}
expr(foo(a = !!xy, b = !!yz))
```

(Or is there a way to use abc to generare names?)

2. The following calls print the same but are different.

```{r}
(a <- expr(mean(1:10)))
#> mean(1:10)
(b <- expr(mean(!!(1:10))))
#> mean(1:10)
identical(a, b)
#> [1] FALSE
```

Whats the difference, which one is more natural?

```{r}
lobstr::ast(!!a)
```

```{r}
lobstr::ast(!!b)
```

 I dont know which is more natural. The solution suggests that `a` is more natural but I think 'it depends'
 
 
## 19.6.5 Exercises

1. Explain how this implementation of exec works:

```{r}
exec <- function(f, ..., .env = caller_env()) {
  args <- list2(...)
  do.call(f, args, envir = .env)
}
```

It uses list2 to enable dynamic dots on the arguments, and then uses base r's do.call to call the function with those args.

2.Skip

3. Explain the problem with this implementation of `set_attr`


```{r}
set_attr <- function(x, ...) {
  attr <- rlang::list2(...)
  attributes(x) <- attr
  x
}
set_attr(1:10, x = 10)
#> Error in attributes(x) <- attr: attributes must be named
```
 
the `x` in `attr` is evaluated to the same value as the `x` in the first argument. I guess that is why so many tidy functions use `.x` so that it not a common variable name and by convention you should not otherwise use these i guess?

## Map -reduce example

```{r}
intercept <- 10
coefs <- c(x1 = 5, x2 = -4)
coef_sym <- syms(names(coefs))

## generate list of expressions (terms)
summands <- purrr::map2(coef_sym, coefs, ~ expr((!!.x * !!.y)))
summands <- c(intercept, summands)
 
## Reduce

eq <- purrr::reduce(summands, ~ expr(!!.x + !!.y))
eq

```


More generally:

```{r}
linear <- function(var, val) {
  var <- ensym(var)
  coef_name <- map(seq_along(val[-1]), ~ expr((!!var)[[!!.x]]))

  summands <- map2(val[-1], coef_name, ~ expr((!!.x * !!.y)))
  summands <- c(val[[1]], summands)

  reduce(summands, ~ expr(!!.x + !!.y))
}

linear(x, c(10, 5, -4))
#> 10 + (5 * x[[1L]]) + (-4 * x[[2L]])
```


## 19.7.5 Exercises

1. I like the 'template' approach, it seems more readable.

2. Reimplement box - cox transform using `new_function`

```{r}
bc <- function(lambda) {
  new_function(exprs(x =), 
  if (lambda == 0) {
    expr({log(x)})
  } else {
    expr( { (x ^ (!!lambda )- 1) / !!lambda })
  })
}
```


3.skip




