# Chapter 20 selected exercises

```{r}
library(rlang)
library(purrr)
```


## 20.2.4

1)  `source` takes an argument called `local` that can have three values:

- True: use the environment from which it is called
- False: Use global
- an environment

2) 
4
4
and just the expression without the outer `expr`.

## 20.3.6

1)   q1 -> 1
     q2 -> 11
     q3 -> 111

2)
```{r}
enenv <- function(arg) {
  qarg <- enquo(arg)
  get_env(qarg)
}
```


## 20.4.6

1) So that later transforms can make use of earlier ones.

3) Is pretty cool, see solution manual

## 20.5.4 

1)  The original threshold_var uses `[[` . I dont know why they coerced it to a string, it works even if you dont.

```{r}

sample_df <- data.frame(a = 1:5, b = 5:1, c = c(5, 3, 1, 4, 1))

subset2 <- function(data, rows) {
  rows <- enquo(rows)
  rows_val <- eval_tidy(rows, data)
  stopifnot(is.logical(rows_val))

  data[rows_val, , drop = FALSE]
}

threshold_var <- function(df, var, val) {
  var <- as_string(ensym(var))
  subset2(df, .data[[var]] >= !!val)
}


df <- data.frame(x = 1:10)
threshold_var(df, x, 8)
```

the new version is, and doesn't need to convert var to a string to use `[[` since it uses `$` instead..  

```{r}
threshold_var <- function(df, var, val) {
  var <- ensym(var)
  subset2(df, `$`(.data, !!var) >= !!val)
}

df <- data.frame(x = 1:10)
threshold_var(df, x, 8)
```

 

## 20.6.3 
Skipping all these base R things.  read the solutions though.

However i copy in the solution for number 3 for future reference, it is useful!

```{r}
lm_wrap <- function(pred, resp = mpg, data = mtcars, 
                    env = caller_env()) {
  pred <- enexpr(pred)
  resp <- enexpr(resp)
  data <- enexpr(data)
  
  formula <- expr(!!resp ~ !!pred)
  lm_call <- expr(lm(!!formula, data = !!data))
  eval(lm_call, envir = env)
}

 
```


This allows you to write  `lm(mpg ~ disp, data = mtcars)` as `lm_wrap(disp)`  which is useful if you are testing a lot of models that only differ by the predictors!
