# Chapter 18 Selected exercises


```{r}
library(rlang)
library(purrr)
```

## 19.3.6 Quoting


1. How is `expr()` implemented ? 

It is simply `\(e) { enexpr(e)}`

2. Compare and contrast two functions below.  Can you predict the output?

(discuss before evaluating)
 
```{r}
f1 <- function(x, y) {
  exprs(x = x, y = y)
}
f2 <- function(x, y) {
  enexprs(x = x, y = y)
}
f1(a + b, c + d)
f2(a + b, c + d)
```

3. Enexpr requires its (immediate) argument to be a symbol not an expression. 

```{r}
(\(x){enexpr(2*x)})(b)
```

If the expression is missing, it returns a 'missing argument' whatever that is. Rlang has a function `is_missing()` to detect that. Copied from the solution:

```{r}
on_missing <- function(x) {enexpr(x)}
on_missing()
is_missing(on_missing())
```

4. Howw are `exprs(a)` and `exprs(a=)` differnet?    
The first one returns a list with a single unnamed elemebt 'a'.  The second returns a list with a single named element $a, with no value. 
 
 
5. `exprs` has more arguments, e.g. `.named` will generate names using for unnamed arguments. 

```{r}
exprs(a, .named = TRUE)
```

6. Skipping


## 19.4.8 Exercises

1. Given the following defintions:

```{r}
xy <- expr(x + y)
xz <- expr(x + z)
yz <- expr(y + z)
abc <- exprs(a, b, c)
```

Use quasiquotation to generate the following calls:

```
(x + y) / (y + z)
-(x + z) ^ (y + z)
(x + y) + (y + z) - (x + y)
atan2(x + y, y + z)
sum(x + y, x + y, y + z)
sum(a, b, c)
mean(c(a, b, c), na.rm = TRUE)
foo(a = x + y, b = y + z)
```

```{r}
expr(!!xy/!!yz)
```

```{r}
expr(-(!!xy)^!!yz)
```

```{r}
expr(((!!xy)) + !!yz - !!xy )
```

Note the double parens. Why?


```{r}
expr(atan2(!!xy,!!yz))
```

```{r}
expr(sum(!!xy,!!xy, !!yz))
```

```{r}
expr(sum(!!!abc))
```

```{r}
expr(mean(c(!!!abc), na.rm = TRUE))
```

```{r}
expr(foo(a = !!xy, b = !!yz))
```

(Or is there a way to use abc to generare names?)

2. The following calls print the same but are different.

```{r}
(a <- expr(mean(1:10)))
#> mean(1:10)
(b <- expr(mean(!!(1:10))))
#> mean(1:10)
identical(a, b)
#> [1] FALSE
```

Whats the difference, which one is more natural?

```{r}
lobstr::ast(!!a)
```

```{r}
lobstr::ast(!!b)
```

 I dont know which is more natural. The solution suggests that `a` is more natural but I think 'it depends'
