# Chapter 18 Selected exercises


```{r}
library(rlang)
library(purrr)
```

## 19.3.6 Quoting


1. How is `expr()` implemented ? 

It is simply `\(e) { enexpr(e)}`

2. Compare and contrast two functions below.  Can you predict the output?

(discuss before evaluating)
 
```{r}
f1 <- function(x, y) {
  exprs(x = x, y = y)
}
f2 <- function(x, y) {
  enexprs(x = x, y = y)
}
f1(a + b, c + d)
f2(a + b, c + d)
```

3. Enexpr requires its (immediate) argument to be a symbol not an expression. 

```{r}
(\(x){enexpr(2*x)})(b)
```

If the expression is missing, it returns a 'missing argument' whatever that is. Rlang has a function `is_missing()` to detect that. Copied from the solution:

```{r}
on_missing <- function(x) {enexpr(x)}
on_missing()
is_missing(on_missing())
```

4. Howw are `exprs(a)` and `exprs(a=)` differnet?    
The first one returns a list with a single unnamed elemebt 'a'.  The second returns a list with a single named element $a, with no value. 
 
 
5. `exprs` has more arguments, e.g. `.named` will generate names using for unnamed arguments. 

```{r}
exprs(a, .named = TRUE)
```

6. Skipping




