## Chapter 6 Functions

### Some key points:

* Function arguments are evaluated lazily 
* Functions are first class
* key parts of a function
   * Formals
   * Body
   * Environment

* Unevaluated arguments are called Promises (e.g. Thunks in Haskell), containing:
   * expression to be evaled
   * environment
   * memoized values
   
* Promises are like a quantum state: any attempt to inspect them with R code will force an immediate evaluation 

* Functions can be of 4 forms: prefix, infix, replacement, and special

In contrast to what the book says, for replacement form, the first argument doesnt have to be `x`. But the second does as it is not called as a positional argument.
```{r}
`second<-` <- function(tt, value) {
  tt[2] <- value
  tt
}
```

* No tail call optimization

### Selected exercises

#### 6.1

4) is.function and is.primitive

```{r}
objs <- mget(ls("package:base", all = TRUE), inherits = TRUE)
funs <- Filter(is.function, objs)

num_args <- lapply(funs, \(x) length(formals(x)))
df <-  data.frame(fun_name = names(num_args), args = as.numeric(num_args))
df <- df[order(df$args, decreasing = TRUE),]
head(df)
```


Scan is the function with the most arguments.

```{r}
nrow(df[df$args == 0,])
```

251 functions with no arguments

for primitive functions:

```{r}
objs <- mget(ls("package:base", all = TRUE), inherits = TRUE)
funs <- Filter(is.primitive, objs)
```

I am not aware of any way to find the number of arguments

#### 6.4

3)  I got 202

```{r}
f <- function(x) {
  f <- function(x) {
    f <- function() {
      x ^ 2
    }
    f() + 1
  }
  f(x) * 2
}
f(10)
```

#### 6.5

3) The function returns c(2,1)  and y is unchanged after exit. The principle is that assigning to a default argument earlier in the argument list provides a value for the default argument. 

```{r}
y <- 10
f1 <- function(x = {y <- 1; 2}, y = 0) {
  c(x, y)
}
f1()
y
```


4)  The xlim default value is not evaluated until it is needed (lazy evaluation). By that time the function has used the default argument `breaks == "Sturges"` to compute a correct value for `breaks` (using `nclass.Sturges`) that can be used as `xlim`. Incidently this function is: `ceiling(log2(length(x)) + 1)`

5) The function works because when `x` is evaluated, `stop` has been redefined to use `Sys.time()`. It is confusing because lookign at the signature of the function you would assume passing in no value for `x` is an error due to the `stop("Error!")`

6) None. If called with  no arguments, it returns a   page of packages available (in the source it checks if `library` is missing.)

#### 6.6

1) For the first part:
```{r}
sum(1, 2, 3)
#> [1] 6
mean(1, 2, 3)
#> [1] 1
```


sum takes `...` to sum up all the arguments, while mean takes a vector and the `...` are used for optional arguments (its an S3 method)

For the second part:
```{r}
sum(1, 2, 3, na.omit = TRUE)
#> [1] 7
mean(1, 2, 3, na.omit = TRUE)
#> [1] 1
```

Sum is tries to add all its arguments, and `na.omit` which is not one of the default arguments (`na.rm` is) TRUE is converted to 1 and added to the rest.
Mean only takes teh mean of the first argument, na.omit is ignored

 
2) To find the docs, look at ?par

3) I believe it is so that you can color the points differently (you can pass a list). I dont know how to color the axes though. Probably with `axis`.  Matlab influenced i presume.

##6.7

1) A character vector of the names of objects created, invisibly. Invisible since you normally are only calling `load` for the side effects.

2) write.table returns NULL. It might more usefully return the table string.

3) Only difference is with_dir lets you specify an arbitrary working directory, while chdir is a boolean and will change to the directory of the source file if TRUE.

4) I don't know enough about base R graphics to do this, but I did look at the solution.

5) 

```{r}
capture.output2 <- function(code) {
  temp <- tempfile()
  on.exit(file.remove(temp), add = TRUE, after = TRUE)

  sink(temp)
  on.exit(sink(), add = TRUE, after = TRUE)

  force(code)
  readLines(temp)
}
capture.output2(cat("a","b","c", sep = '\n'))
```

The results of capture.output2 are the same as capture.output in this case.

`capture.output` has additional options (for example, the name of the capture file) but works the same as far as I can tell. It looks like this:

```
function (..., file = NULL, append = FALSE, type = c("output", 
    "message"), split = FALSE) 
{
    type <- match.arg(type)
    rval <- NULL
    closeit <- TRUE
    if (is.null(file)) 
        file <- textConnection("rval", "w", local = TRUE)
    else if (is.character(file)) 
        file <- file(file, if (append) 
            "a"
        else "w")
    else if (inherits(file, "connection")) {
        if (!isOpen(file)) 
            open(file, if (append) 
                "a"
            else "w")
        else closeit <- FALSE
    }
    else stop("'file' must be NULL, a character string or a connection")
    sink(file, type = type, split = split)
    on.exit({
        sink(type = type, split = split)
        if (closeit) close(file)
    })
    for (i in seq_len(...length())) {
        out <- withVisible(...elt(i))
        if (out$visible) 
            print(out$value)
    }
    on.exit()
    sink(type = type, split = split)
    if (closeit) 
        close(file)
    if (is.null(rval)) 
        invisible(NULL)
    else rval
}
```
#### 6.8

1)
```{r}
`+`(`+`(1,2),3)
`+`(1,`+`(2,3))

x= c(1,2,3,4,5,6)
n=4

`if`(length(x) <= 5,`[[`(x,5),`[[`(x,n))
```
2) 
The first one , the 20 is the first positional argument and so is `x` in the call. The same principle applied to `runif`.  
For `cor`,  remember that arguments are first matche exactly, then by partial match, and then by position. This results in the call:
```
cor(x, y, use = "pairwise.complete.obs", method = "kendall") 
``` 
(The match on the `method` and `use` is due to using pmatch/match in the function def, although i am not sure about that.)

3) 
```{r}
x = c(1,2,3,4,5,6)
`modify<-` <- function(x, position, value) {
  x[position] <- value
  x
}
modify(get('x'), 1) <- 10
```

My answer: This fails because get("x") evalutes to a value (rvalue) and not a symbol
Solution: get("x") is not evaluated, but rather in this context the expression is expanded to: 
```
get("x") <- `modify<-`(get("x"), 1, 10)
```
and it then tries to expand to `get<-` which doesnt exist.


4) 
```{r}
x = c(1,2,3,4,5,6)
`rmodify<-` <- function(x, value) {
  position <- sample(seq_along(x),1)
  x[position] <- value
  x
}
rmodify(x) <- 10
x
```

5)
```{r}
`+` <- \(a,b){
  if(is.character(c(a,b))){
    paste(a,b,sep ="")
  } else {
    base::`+`(a, b)
  }
}

1 + 2

"a" + "b"

rm(`+`)
```

6)
I couldnt figure out how to restrict to base package without looking at the solution, sadly.


```{r}
repl <- apropos("<-", where = TRUE, mode= "function")
repls_base <- repls[names(repl) == length(search())]
length(repls_base)
 
```

SO there are 63 replacement functions in the base package. Which are primitive? (COPY PASTA FROM SOLUTION)

```{r}
repls_base_prim <-Filter(is.primitive, mget(repls_base, envir = baseenv())) |>
  names()
```

This seems to require knowledge that will be gained in later chapters. 

7) Infix can be any sequence of characters between the '%' except '%'.

8) 
```{r}
`%xor%` <- \(x,y){
  xor(x,y)
}

TRUE %xor% FALSE
```



9)  
 Used %//% because %/% is integer divide
 
```{r}
`%n%` <- \(A,B) intersect(A,B)
`%u%` <- \(A,B) union(A,B)
`%//%` <- \(A,B) setdiff(A,B)

x <- c(1,2,3,4,5,6)
y <- c(2,4,6,8)

x%n%y
x%u%y
x%//%c(1,2,3)

 
```

