## Chapter 7 Environments

### Selected exercises

#### Section 7.2

1. Environments use reference semantics,  names are unordered, names must be unique

2. 
```{r}
library(rlang)
test_env <- env()
test_env$loop <- test_env
```

3.
```{r}
env1 <-env()
env2 <-env(dedoop = env1)
env1$loop <- env2
```

4. 
- e[[1]]  doesnt make sense because the names are unordered in an environment
- e[c("a", "b")] would need to return two elements.  I suppose it could   create a sub environment with just those names, makes sense to me. Or a list. So I dont agree that it 'doesn't make sense'

5.
Create a version of env_poke() that will only bind new names, never re-bind old names. Some programming languages only do this, and are known as single assignment languages.

```{r}
env_poke_5 <- function(env = caller_env(), nm, value){
  if(env_has(nm))
     stop('name exists')
  env_poke(env,nm,value)
  invisible(env)
}

```

6) What does this do and how does it differe from `<<-`.  Why might you prefer it.

This function is like `<<-` except if there is no binding it will not bind in the global environment. This prevents some errors , since you almost never intend to bind into the global environemnt when using `<<-`.

```{r}
rebind <- function(name, value, env = caller_env()) {
  if (identical(env, empty_env())) {
    stop("Can't find `", name, "`", call. = FALSE)
  } else if (env_has(env, name)) {
    env_poke(env, name, value)
  } else {
    rebind(name, value, env_parent(env))
  }
}
rebind("a", 10)
#> Error: Can't find `a`
a <- 5
rebind("a", 10)
a
#> [1] 10
```

#### 7.3


 