# Chapter 14 (selected exercises)


```{r}
library(R6)
```


## 14.2.6 

1.
```{r}
BankAccount <- R6::R6Class("BankAccount",
                           public = list(
                             deposit = \(amount) {
                               if(amount > 0)
                                   private$balance_ = private$balance_ + amount
                               else 
                                   stop("Can't deposit a negative amount", call. = FALSE)
                             },
                             withdraw =  \(amount) {
                               if(amount > 0)
                                   private$balance_ = private$balance_ - amount
                               else 
                                   stop("Can't withdraw a negative amount", call. = FALSE)
                             }),
                           private = list(
                             balance_ = 0
                           ),
                           active = list(
                             balance = \(value){
                               if(missing(value)){
                                 private$balance_
                               } else {
                                 stop("Balance is read only", call. =FALSE)
                               }
                             }
                           )
)


BankAccountLimited <- R6::R6Class("BankAccountLimited",inherit = BankAccount,
                                  public = list(
                                    withdraw = \(amount){
                                      if(amount > private$balance_)
                                         stop("You cannot withdraw more then you have!", call. = FALSE)
                                      else 
                                        super$withdraw(amount)
                                    }
                                  ))

## Skipping the third case
```

Testing

```{r}
test <- BankAccountLimited$new()
test$deposit(1000)
test$balance
```

```{r}
test$withdraw(999)
test$balance
```

```{r}
test$withdraw(10)
test$balance
```


3. You *can* model these with s3 class, you just have to pass state along on every call. But it is more straightforward as R6 class.

7. 
```{r}
typeof(test)
```

```{r}
attributes(test)
```

## 14.3.3

1) did this already

4) Can subclasses access private fields/methods from their parent?

Well, they sure can, see my bank account , which relies on accessing the private balance! However the answer tries to do it with 'super' which is kind of wierd.



 



