# Chapter 11 exercises


```{r}
library(rlang)
library(ggplot2)
library(dplyr)
library(purrr)
```

## 11.2.3 Exercise 

1) `Vectorize()` is a wrapper that takes a function and 'vectorizes' so that it works properly (elementwise) when applied to a vector. Internally it uses a mapply.

2) `possibly()` internally uses a try catch. returning the `otherwise` argument when a failure occurs.

3) `safely()` uses `capture_error`, which I could not find documented anywhere, it is in namespace:purr : 

```{r}
environment(safely)$capture_error
```
So once again `tryCatch` is used, forming the appropriate lists in each case. Note that `code` is not forced, lazy evaluation is being taken advantage of in this case.

NB: Looking at solution i found you can also access these namespaces with three colons `purrr:::capture_output`.

###  Exercises 11.3.1

1) To my mind, you would like the dot to appear right after each file is downloaded so you can see progress. 

2) I don't think you should memoise download.file as the data at  the url might change and you would like to capture that!

* skipped 3 and 4 

5)

```{r}
delay_by <- function(f, amount) {
  force(f)
  force(amount)
  current_time <- NULL
  function(...) {
    if(!is.null(current_time))
    {
    delay <- amount - (as.numeric(Sys.time())- current_time)
    } else {
    delay <- amount
    }
    if(delay >0)
        Sys.sleep(delay)
    
    
    # note solution manual used on.exit to make this happen after f, which is another intepretation
    current_time <<- as.numeric(Sys.time())
    f(...)
  }
}
system.time(runif(100))

system.time(delay_by(runif, 0.1)(100))

g <- delay_by(runif,1) 
system.time({g(100);Sys.sleep(2);g(100)})
```





