# Chapter 13 (selected exercises)

## 13.2.1 

```{r}
library(sloop)
library(rlang)
```


1. `t.test` is a generic, which does the student t.test  on objects based on what class they are. `methods` suggests that there is only the default and `formula`. 

`t.data.frame` is a method (for class data.frame, method t = transpose)

5. 
```{r}
x <- ecdf(rpois(100, 10))
class(x)
```

looks like it must be based on a function. Which makes sense

```{r}
typeof(unclass(x))
```

Interesting. I think this is because there is no other way to make a callable object.  Not sure though.

```{r}
attributes(x)
```

6. 

```{r}
x <- table(rpois(100,5))
class(x)
```

```{r}
typeof(unclass(x))
```

Underlying type is an integer array


```{r}
attributes(x)
```

## 13.3.4

*skipping*, but I did look at the solution to #1. 

They did not approach it the way i would have! I would have used ... to allow construction in the same way that lists are constructed.


## 13.4.4.

1.) t.test just calls `UseMethod` so yes, it is an S3 Generic. (For t-tests)
The following code with class test will call the method t.test (for the tranpose generic `t`) and since `t.test` doesn't exist, it will end up calling the default and taking the transpose of x.

```{r}
x <- structure(1:10, class = "test")
t(x)
```


2.) 
```{r}
s3_methods_class("table")
```

3) 
```{r}
s3_methods_class("ecdf")
```


4) Skipping, but I would guess `print`, since it has 245 !

5) 
```{r}
g <- function(x) {
  x <- 10
  #browser()
  y <- 10
  UseMethod("g")
}
g.default <- function(x) c(x = x, y = y)

 

x <- 1
y <- 1
g(x)
#>  x  y 
#>  1 10
#>  
#>  
```


So x has no class, so we expect g.default to be called by UseMethod. At this point we are in an environment where x and y have both been defined to be 10.  Yet the x <- 10 does not mask  the argument value of x.   The documentation does not make this crystal clear, the closest i could find is : "UseMethod creates a new function call with arguments matched as they came in to the generic. Any local variables defined before the call to UseMethod are retained (unlike S).".  

It must be low level magic because the value is definatly overwritten in the environment.  



6) `[` must be a primitive generic, as it has methods ,but the source just says it is primitive. The solution is not much help, its a mess. 

## 13.5.1

1) I will look at  a few. 

- `I`.  I() returns an object of class `AsIs`.  All it does it add "AsIs" to the classes on the object, and the underlying object is otherwise returned AS IS.   

- `ecdf` we looked at this before, it is built on functions

- `lm` : 

```{r}
mod <- lm(x~ y, data = data.frame( x= 1:10, y=1:10))
class(mod)
```


```{r}
typeof(unclass(mod))
```

Perhaps unsuprisingly lm is built on. a list, but as a scalar object type   (they are not equal length)

2).  Continuing with lm, lets continue to try to take it apart.

```{r}
rawlm <- unclass(mod)
attributes(rawlm)
```
So the lm really is just a list, with each of the necessary values .

We would need to fill a list with all these things and then add the class lm. 


## 13.6.3

1.  [.Date looks like this:

```
function (x, ..., drop = TRUE) 
{
    .Date(NextMethod("["), oldClass(x))
}

```

Looks like it uses oldClass (which i guess pulls the class? But differently then class() ? ) to reconstruct a date from whatever is returned from NextMethod, so this supports inheritence.  How it fails? The solution mentions that other attributes of the object besides the class that are used by the subclass are lost!

2. SKIP

3. 
```{r}
generic2 <- function(x) UseMethod("generic2")
generic2.a1 <- function(x) "a1"
generic2.a2 <- function(x) "a2"
generic2.b <- function(x) {
  class(x) <- "a1"
  NextMethod()
}

generic2(structure(list(), class = c("b", "a2")))

```

I would expect it to return `a2` based on what the text said about the weird way NextMethod works (i.e. uses the original class list.). And it does. 



