# Chapter 10
```{r}
library(rlang)
library(ggplot2)
library(scales)
library(dplyr)
library(purrr)
```

## Exercises

### 10.2.6

1). using `force` makes the intention clear

2).

approxfun takes data points and returns an interpolating function.

ecdf takes data (observations) and returns the empirical distribution function. It is a function (closure) but also is an S3 object which is interesting. 
```{r}
fake = rnorm(100)
fake.ecdf = ecdf(fake)
fake.ecdf(0)
```


3). 
```{r}

pick <- \(i) {
  force(i)
  \(x) x[[i]]
}


example <- c(1,2,3,4)
pick(2)(example)
#lapply(mtcars, pick(5))

```

4).

```{r}
moment <- \(i){
  force(i)
  \(vec) sum((vec - mean(vec)) ^ i) / length(vec)
}

m1 <- moment(1)
m2 <- moment(2)

x <- runif(100)
stopifnot(all.equal(m1(x), 0))
stopifnot(all.equal(m2(x), var(x) * 99 / 100))
```

5)

If you dont use a closure, then you will really only have one counter.

6)

If you don't use `<<-` then you will only create a new `i` in the execution environment and the counter will not increment. It will always return '1'

```{r}
new_counter3 <- function() {
  i <- 0
  function() {
    i <- i + 1
    i
  }
}

c1 = new_counter3()
for (i in 1:3)
   print(c1())


```


### 10.3.4 *skipping* (but read solution manual)


### 10.4.4

1) `df` and `formula` are evaluated when it is used to fit the model.   No need to force it.

2) The difference here is that `boxcox3` takes the data and returns a function of lambda (opposite of what `boxcox2` did). You might want to do this to try out different lambdas on your data set (which is not changing)

3) It is not a true 'copy' but rather points to the same data (copy on modify)

4)

```{r}
ll_poisson1 <- function(x) {
  n <- length(x)

  function(lambda) {
    log(lambda) * sum(x) - n * lambda - sum(lfactorial(x))
  }
}

ll_poisson2 <- function(x) {
  n <- length(x)
  sum_x <- sum(x)
  c <- sum(lfactorial(x))

  function(lambda) {
    log(lambda) * sum_x - n * lambda - c
  }
}

ns <- 2^seq(1,14)

bench_res <- tibble(ns = ns)

bench_test <- function(method) {
  function(n){ 
    x<- rpois(n, lambda=1)
    ll <- method(x)
    res <- bench::mark(ll(1))
    res$median
  }
}

bench_res <- bench_res |>   mutate(method1 = map_dbl(ns,bench_test(ll_poisson1)),
                      method2 = map_dbl(ns,bench_test(ll_poisson2)))

```

```{r}
bench_res |> ggplot(aes(x=ns)) +
     geom_line(aes(y=method1)) + 
     geom_line(aes(y=method2), color = 'blue') + scale_y_log10()
```

Method 2 is much faster and the speed doesnt depend on `n` since the computations are only done once.

### 10.5.1

1) e, it depends on if `f` or `z` is defined in `x`.   

2) *** skipping, read answer ***

 
