## Chapter 7 Environments

### Selected exercises

#### Section 7.2

1. Environments use reference semantics,  names are unordered, names must be unique

2. 
```{r}
library(rlang)
test_env <- env()
test_env$loop <- test_env
```

3.
```{r}
env1 <-env()
env2 <-env(dedoop = env1)
env1$loop <- env2
```

4. 
- e[[1]]  doesnt make sense because the names are unordered in an environment
- e[c("a", "b")] would need to return two elements.  I suppose it could   create a sub environment with just those names, makes sense to me. Or a list. So I dont agree that it 'doesn't make sense'

5.
Create a version of env_poke() that will only bind new names, never re-bind old names. Some programming languages only do this, and are known as single assignment languages.

```{r}
env_poke_5 <- function(env = caller_env(), nm, value){
  if(env_has(nm))
     stop('name exists')
  env_poke(env,nm,value)
  invisible(env)
}

```

6) What does this do and how does it differe from `<<-`.  Why might you prefer it.

This function is like `<<-` except if there is no binding it will not bind in the global environment. This prevents some errors , since you almost never intend to bind into the global environemnt when using `<<-`.

```{r}
rebind <- function(name, value, env = caller_env()) {
  if (identical(env, empty_env())) {
    stop("Can't find `", name, "`", call. = FALSE)
  } else if (env_has(env, name)) {
    env_poke(env, name, value)
  } else {
    rebind(name, value, env_parent(env))
  }
}
rebind("a", 10)
#> Error: Can't find `a`
a <- 5
rebind("a", 10)
a
#> [1] 10
```

#### 7.3
1)

Note that you can use an accumulator argument here too, which would make it tail recursive. R doesn't do tail call optimization so it doesnt matter. 


```{r}
where <- function(name, env = caller_env()) {
  if (identical(env, empty_env())) {
    # Base case
    NULL
  } else if (env_has(env, name)) {
    # Success case
    c(where(name, env_parent(env)), env)
  } else {
    # Recursive case
    where(name, env_parent(env))
  }
}


env2 = env( stop = "test")

where("stop", env2)
```

2)

```{r}
fget <- function(name, env = caller_env(), inherits= TRUE) {
  if (env_has(env, name) && is_function(env_get(env,name))) {
    env
  } else {
    # Recursive case
    if(inherits && !identical(env, empty_env()))
       fget(name, env_parent(env))
    else
      stop("Funcion not found: ", name, call.= FALSE)
  }
}

fget("stop", env2)
```

#### 7.4

1) How is search_envs() different from env_parents(global_env())?

search_envs() includes global_env, but not the empty_env at the root. env_parents(global_env()) doesnt include the global environment but does include the empty_env that is the root.


3) Write an enhanced version of str() that provides more information about functions. Show where the function was found and what environment it was defined in.
- skipping this one, seems tedious.

#### 7.5

Write a function that lists all the variables defined in the environment in which it was called. It should return the same results as ls().

```{r}
test_call_env <- function()
{
  env_names(caller_env())
}

test_call_env()
```


 