## Function operator: Compose

An example of a function operator that is *not* a "decorator is *function composition*

The composition of a function $f$ with a function $g$ is usually denoted by

$$
h = g \circ f
$$

The meaning is that $h(x) = g(f(x))$.   We can express this in `r` as a function operator:

```{r}
`%o%` <-function(f,g) function(...) f(g(...))

fourthroot <- sqrt %o% sqrt
fourthroot(16)

```

`purrr::compose` does this same thing (but with more flexibility and safety.)

```{r}
not_null <- purrr::compose(`!`, is.null)
not_null(4)
not_null(NULL)
```


This can be useful, and in some languages (e.g. Haskell) the composition operator takes a central role (it's expressed by `.`), but in `r` this kind of idea is instead more commonly expressed  by the pipe:

```{r}
16 |> sqrt() |> sqrt()
```

The pipe operates on unevaluated expressions (promises), not functions.   It seems like magic right now, so I look forward to learning more in the Metaprogramming section of advanced r! 

 
